In retail and e-commerce context, the organization scope we deal with in this project mainly include e-commerce sales,
customer service and marketing, hence make the sales and marketing teams along with stakeholders and managers the target
user of data. Based on the organization’s operational needs and strategic objectives, we identified several key business
requirements:
\begin{itemize}
    \item 
Data-driven decision-making: The organization needs to be able to analyze large datasets quickly and efficiently to make 
informed decisions that improve customer satisfaction, increase revenue, and enhance operational efficiency.
\item Real-time insights: Decision-makers require up-to-date information on sales performance, inventory levels, and customer
sentiment to act quickly and adjust strategies when needed.
\item Data visualization: Stakeholders at various levels of the organization need intuitive and actionable insights, which 
can be best achieved through clear data visualizations and dashboards.
\item Scalability: As the organization expands, its data storage and processing requirements will grow, requiring a technology
solution that can scale seamlessly to handle increasing data volumes.
\end{itemize}
To address these business requirements, we assessed the following big data characteristics:
\begin{itemize}
\item Volume: The organization generates a massive amount of data daily, from transactional data in sales to the grow in quantity
of customer and product records as the organization continues to scale out. This requires a solution that can store and process
large datasets without performance degradation
\item Velocity: The speed at which data is generated, particularly from sales transactions, inventory updates, and customer
 interactions, requires real-time processing and immediate insights for decision-making.
\item Value: The organization needs to extract meaningful insights from large datasets to drive revenue growth, improve
customer retention, and optimize operations. Without value-driven insights, big data would be just raw information.
\item Veracity: Due to various source of information and method of data collection, the data can observe abnormalities and
noise. To provide valuable insights for sale and marketing activities, the need to ensure veracity is stressed as biased 
insights can lead to business decline.
\end{itemize}
\newpage
