\subsection{Input}
The primary input for this data warehouse solution consists of comprehensive sales activities data,
encompassing three main data categories: products, customers, and transactions. These data streams
form the foundation for the analytical services and represent the core business activities that need
to be processed and analyzed.

Product data includes detailed information across 73 different dimensions, capturing essential
attributes such as product descriptions, brand information, manufacturing dates, pricing, and
current status. This extensive product dataset comprises approximately 700,000 entries per CSV file,
providing a rich source of information for product-related analytics and inventory management
insights.

Customer data is even more extensive, spanning 87 dimensions that encompass crucial customer
information including personal details, geographical locations, demographic background, loyalty
membership status, and contact information. With over 4.7 million entries, this customer dataset
provides a comprehensive view of the customer base, enabling detailed customer segmentation and
personalized analysis. Additionally, transaction data is structured in a header-lines table design
pattern, where sale headers contain 21 dimensions of invoice-level information, and sale lines
include 26 dimensions of item-level transaction details.

\subsection{Output}
The data warehouse solution is designed to deliver three primary outputs that provide significant
business value: analytics dashboards, consulting services, and customer recommendations. These
outputs are carefully crafted to transform raw sales data into actionable insights and valuable
business intelligence.

The analytics dashboards serve as a comprehensive visualization tool that leverages the various
dimensions of each data file to present a holistic view of the business. These dashboards are
specifically designed to be human-readable and enable easy analysis of sales performance, key
performance indicators (KPIs), and other critical business metrics. Through these interactive
dashboards, stakeholders can effectively monitor business performance and identify trends or
patterns in their sales data.

The system also provides customer recommendations through its near real-time processing
capabilities. Each customer transaction is collected and processed to continuously update the
Customer Data Platform (CDP), enabling a more comprehensive single view of the customer.
Additionally, the solution offers consulting services that go beyond descriptive analytics by
incorporating machine learning techniques for predictive analysis. These advanced analytics
capabilities help generate deeper business insights, enabling more informed decision-making and
strategic planning.